---
title: "EarableManuscriptFigures"
output: html_document
---

# Setup - set directory, load libraries, set figure locations

```{r setup, include=FALSE}

setwd("~/Downloads/EarableManuscript_2021")
rm(list=ls())

# loading needed libraries
if (!requireNamespace("BiocManager", quietly = TRUE))
install.packages("BiocManager")

# remotes::install_github("ying14/yingtools2")
# install.packages("ifultools", repos="http://R-Forge.R-project.org")
# install.packages("pacman")

pacman::p_load(
  dplyr,yingtools2,data.table,ifultools,stringr,
  ggplot2,Hmisc,tidyr,hues,tidyverse,
  circlize,ComplexHeatmap,viridis,RColorBrewer,
  umap,ggpubr,factoextra,phyloseq,
  reshape2,EnvStats,lme4,
  grid,sjstats
  )

mainDir <- "./"
fig_folder <- paste(mainDir,"Figures/",sep="")
dir.create(file.path(mainDir,fig_folder), showWarnings = TRUE,recursive = TRUE)

```

# Write out and read in manuscript data

```{r}

filenames <- list.files("./Earable_Dec2021/", full.names = TRUE, recursive = TRUE)
filenames

processed_data <- tibble(File = filenames) %>%
  extract(File, "Name", "(?<=./Earable_Dec2021//)(.*)(?=.csv)", remove = FALSE) %>%
  dplyr::mutate(Data = lapply(File, read.csv)) %>%
  unnest(Data) %>%
  select(-File)

processed_data$X <- NULL
n_last <- 24
processed_data$Name <- substr(processed_data$Name, 1, nchar(processed_data$Name))
processed_data$Name <- gsub("\\/","",processed_data$Name)
processed_data$Name <- gsub("\\_variables","",processed_data$Name)
processed_data <- processed_data %>% separate(Name, sep ="_(?=[^_]+$)",into=c("Person","time"))

write.table(processed_data,"Earable.Dec2021.processed.data.all.tsv",sep = "\t",quote = F,row.names = F)

```

```{r}
data <- processed_data

data$sample <- make.names(paste(data$Person,data$time,data$Task.Label,sep = "."),unique = T)

metadata <- data %>% select(sample,Person,time,Task.Label) 
metadata <- metadata %>%
  arrange(time, Person,Task.Label,sample) %>% 
  mutate(sample = factor(sample, unique(sample))) 

samp <-metadata %>% column_to_rownames("sample")

raw_data <- data %>% select(-c(Person,time,Task.Label)) %>% column_to_rownames("sample")  %>% t() 

rownames_metadata <- read.csv(file = "./rownames_Earable_2021.csv",header = T) %>%
  dplyr::rename(otu = feature_name)

```

# Heatmap

```{r}
##################################################

sig_data_c <- raw_data
tm <- match(rownames(samp),names(as.data.frame(sig_data_c)))
sig_data_c<-sig_data_c[,tm]
tmp_c<-samp

mat<-as.matrix(as.data.frame(sig_data_c))  

any(is.na(mat))

mat2 <- t(scale(t(mat))) #take Z score
mat2<- as.matrix(mat2) %>% na.omit()

#convert all values greater or less than 3/-3 to 3
mat2[mat2>=3]<- 3
mat2[mat2<=-3]<- -3

annotation_col <-data.frame(rownames(tmp_c),
                        Person = as.character(tmp_c$Person),
                        time = as.character(tmp_c$time),
                        #task = as.character(tmp_c$Task.Label),
                        row.names = 1)

####### row color annotations ######
match_tax_dt <- data.frame(rownames_metadata) %>% column_to_rownames(var = "otu")
match_tax_dt <- match_tax_dt[order(match_tax_dt$Category,match_tax_dt$Group),]

match_tax_dt$Group %>% unique
super_col <- c("Time"= "#9857ff","Amplitude" = "#8f7536", "Frequency" = "gray",
               "Bandpower" = "#9AAE73","Skew" = "#51AB9B", "Kurtosis" = "#4169E1",
               "Variance" = "#FF69B4","other" = "#f69ea0") 

ha1_left = HeatmapAnnotation(Group = match_tax_dt$Group,
                             col = list(Group = super_col), 
                             annotation_name_side = "bottom",
                             which = "row")

##########################################

person_col <- iwanthue(length(annotation_col$Person %>% unique))
names(person_col) <- annotation_col$Person %>% unique

time_col <- iwanthue(length(annotation_col$time %>% unique))
names(time_col) <- annotation_col$time %>% unique

color_cols <- list(Person = person_col, time = time_col)
ha_column = HeatmapAnnotation(df=annotation_col,col=color_cols,  annotation_name_side ="left",
                              border = FALSE)

split_cols <- tmp_c$Task.Label
split_rows <-  match_tax_dt$Category

ht3 = Heatmap(as.matrix(mat2), name = "z score", column_title = NA, 
              top_annotation = ha_column,
              row_split = split_rows,
              show_parent_dend_line = F,
              left_annotation = ha1_left,
              clustering_distance_rows = "euclidean",
              column_split = split_cols, 
              cluster_column_slices = F, 
              row_title_gp = gpar(fontsize = 10,fontface = "bold"), row_title_rot = 0,
              col = colorRampPalette(rev(brewer.pal(n = 7, name = "RdBu")))(100), 
              width=2, cluster_columns = F, 
              row_names_gp = gpar(fontsize = 9),
              row_names_max_width = max_text_width(rownames(mat), gp = gpar(fontsize = 16)),
              show_column_names = F, 
              show_row_names = F,
              column_names_side = "top",na_col="white",
              column_title_rot = 0,
              heatmap_legend_param = list(title = "z score", at = c(-3,-2,-1,0,1,2,3)))
draw(ht3) 

# pdf(paste(fig_folder,"Heatmap_activity_split.June2021.pdf",sep = "/"),height = 8, width = 15,useDingbats = F)
# draw(ht3) #annotation_legend_side = "bottom"
# dev.off()
```

# UMAP

```{r}
data <-  processed_data 
data$sample <- make.names(paste(data$Person,data$time,data$Task.Label,sep = "."),unique = T)
metadata <- data %>% dplyr::select(sample,Person,time,Task.Label) 
raw_data_umap <- data %>% dplyr::select(-c(Person,time,Task.Label)) %>%
  column_to_rownames("sample")
raw_data_scaled <- scale(raw_data_umap)

umap.defaults
class(umap.defaults)
umap.defaults$min_dist <- 0.5

umap_results <- umap::umap(raw_data_scaled,config = umap.defaults)

umap_plot_df <- data.frame(umap_results$layout) %>%
  tibble::rownames_to_column("sample") %>%
  dplyr::inner_join(metadata, by = "sample")

task_col <- iwanthue(length(metadata$Task.Label %>% unique))
names(task_col) <- metadata$Task.Label %>% unique

time_col <- iwanthue(length(metadata$time %>% unique))
names(time_col) <- metadata$time %>% unique

person_col <- iwanthue(length(metadata$Person %>% unique))
names(person_col) <- metadata$Person %>% unique


#pdf("./Figures/UMAP_Task.pdf",width = 7,height = 5,useDingbats = F)
umap_plot_df %>% 
  mutate(task = metadata$Task.Label) %>%
  ggplot(aes(X1, X2, color = task)) + geom_point(size=2.5) +
  scale_color_manual(values = task_col) + theme_classic() +
  guides(colour = guide_legend(override.aes = list(size=5))) +
  theme(legend.text = element_text(size=15),
        axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=15),
        axis.text.x = element_text(size=15),
        axis.text.y = element_text(size=15)) +
  xlab("UMAP1") + ylab("UMAP2")
# dev.off()

#pdf("./Figures/UMAP_task.pdf",width = 9,height = 5)
umap_plot_df %>% 
  mutate(task = metadata$time) %>%
  ggplot(aes(X1, X2, color = task)) + geom_point(size=2.5) +
  scale_color_manual(values = time_col) + theme_classic() +
  guides(colour = guide_legend(override.aes = list(size=5))) +
  theme(legend.text = element_text(size=15),
        axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=15),
        axis.text.x = element_text(size=15),
        axis.text.y = element_text(size=15)) +
  xlab("UMAP1") + ylab("UMAP2")
# dev.off()

#pdf("./Figures/UMAP_task.pdf",width = 9,height = 5)
umap_plot_df %>% 
  mutate(task = metadata$Person) %>%
  ggplot(aes(X1, X2, color = task)) + geom_point(size=2.5) +
  scale_color_manual(values = person_col) + theme_classic() +
  guides(colour = guide_legend(override.aes = list(size=5))) +
  theme(legend.text = element_text(size=15),
        axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=15),
        axis.text.x = element_text(size=15),
        axis.text.y = element_text(size=15)) +
  xlab("UMAP1") + ylab("UMAP2")
# dev.off()

```

# Feature correlation plot

```{r}
############## Feature correlation plot ######################

x_baseline <- raw_data
# x_baseline <- x_baseline %>% column_to_rownames("otu")

Corr_raw_data <- t(x_baseline)
class(Corr_raw_data)

res2 <- rcorr(as.matrix(Corr_raw_data),type="spearman")

#pdf(paste(fig_folder,"kmeans.K6.Earable.pdf",sep = "/"),height = 3, width = 5,useDingbats = F)
fviz_nbclust(res2$r, kmeans, method = "gap_stat") #default with mat is rows, use t(mat) for cols
dev.off()

#7 is the optimal number of variable clusters at baseline
km.res <- kmeans(res2$r, 6, nstart = 25)
print(km.res)

mat_genes <- as.matrix(res2$r)
keep_names <- colnames(mat_genes)
mat_genes2 <- t(mat_genes)[keep_names,]

#get k means cluster numbers
clusters <- data.frame(cluster_number = km.res$cluster,
                       cluster = km.res$cluster)
clusters <- clusters[order(clusters$cluster_number),]

#order rownames for row annotations and matrix for heatmap 
v1 <- intersect(rownames(clusters),rownames(mat_genes2))
clusters <- clusters[v1,]
mat_genes2 <- mat_genes2[v1,] 
mat_genes2 <- mat_genes2[,v1] 

split_rows <- clusters$cluster_number
split_cols <- clusters$cluster_number

#row annotation
#match_tax_dt <- data.frame(get.tax(phy)) %>% column_to_rownames(var = "otu")
match_tax_dt <- match_tax_dt[v1,] 

super_col <- c("Time"= "#9857ff","Amplitude" = "#8f7536", "Frequency" = "gray",
               "Bandpower" = "#9AAE73","Skew" = "#51AB9B", "Kurtosis" = "#4169E1",
               "Variance" = "#FF69B4","other" = "#f69ea0") 

ha1_left = HeatmapAnnotation(Group = match_tax_dt$Group,
                             col = list(Group = super_col), 
                             annotation_name_side = "bottom",
                             which = "row")
ha1_top = HeatmapAnnotation(Group = match_tax_dt$Group,
                             col = list(Group = super_col))

mat3 <- Heatmap(mat_genes2, name = "Spearman \nCorrelation",
                row_names_side = "left",
                left_annotation = ha1_left, top_annotation = ha1_top,
                row_split = split_rows, column_split = split_cols,
                row_title = c("","","","","",""),
                column_title = c("","","","","",""),
                #left_annotation = ha_row_annotation,
                #bottom_annotation = ha_bottom_annotation,
                col = colorRampPalette(rev(brewer.pal(n = 7, name = "RdBu")))(100),
                show_column_names = F, show_row_names = F,
                column_names_rot = 45,
                cluster_columns = F, cluster_rows = F,
                row_names_max_width = max_text_width(rownames(mat_genes2), gp = gpar(fontsize = 16)),
                column_names_max_height = max_text_width(colnames(mat_genes2), gp = gpar(fontsize = 16)),
                show_parent_dend_line = F,
                heatmap_legend_param = list(at = c(-1,-0.5,0,0.5,1)),
                show_row_dend = F)
#pdf(paste(fig_folder,"Spearman_K6_Earable.Sep2020.pdf",sep = "/"),height = 5, width = 7,useDingbats = F)
mat3
# dev.off()

```

##########################################################################################################################

# Data Preparation

```{r Data Preparation}

##Introduce Demographic Variables
age <- c(28, 61, 33, 27, 28, 18, 27,27,26,46)
height <- c(5*12+11, 5*12+9, 5*12+1, 6*12, 5*12+9, 5*12+6, 5*12+1, 5*12+6, 5*12+3, 5*12+54)
weight <- c(200, 165, 114, 165, 170, 160, 143, 141, 140, 150)
gender <- c("M", "F", "F", "M", "M", "F", "M", "M", "F", "F")

mg0 <- processed_data
id <- unique(mg0$Person)

mg0$age <- c(NA)
mg0$gender <- c(NA)
mg0$height <- c(NA)
mg0$weight <- c(NA)
for (i in 1:10){
  mg0$age[mg0$Person == id[i]] = age[i]
  mg0$gender[mg0$Person == id[i]] = gender[i]
  mg0$height[mg0$Person == id[i]] = height[i]
  mg0$weight[mg0$Person == id[i]] = weight[i]
}


##Compute BMI values
mg0$BMI <- mg0$weight / mg0$height^2 *703
mg <- reshape2::melt(mg0, id.vars = c("Person", "time", "Task.Label", "BMI", "age", "gender","height", "weight"), variable.name = "variables")
var <- as.vector(unique(mg$variables))
task <- sort(as.vector(unique(mg$Task.Label)))
mg <- mg[order(mg$Person, mg$time, mg$Task.Label, mg$variables),]

##Add repeat measurement indexing column
mg <- as.data.frame(mg %>%
            group_by(Person, time, Task.Label, variables) %>%
            mutate(index = seq_along(variables)))

```

# Data Check and Cleaning

```{r Data Check and Cleaning}
##check identical values
ident_var <- list()
colnm <- colnames(mg0[,4:165])
for (i in 1:16){
new_var <- list(colnm[apply(mg0[mg0$Task.Label == task[i],4:165], 2, function(a) length(unique(a))==1)] %>% as.vector())
ident_var <- c(ident_var, new_var)
}
ident_var <- unique(unlist(ident_var))

##check normality
norm_results <- matrix(NA, ncol = 16, nrow = 155)
mg1 <- mg[!mg$variables %in% ident_var,]
var1 <- as.vector(unique(mg1$variables))

for(i in 1:length(var1)){
  for(j in 1:length(task)){
    norm_results[i,j] <- shapiro.test(mg1[mg1$variables == var1[i] & mg1$Task.Label == task[j],]$value)$p.value

  }
}
##Noramlity assumption violated variables and Tasks
sum(norm_results > 0.1)

##scale values by column
neg_var <- as.vector(mg[mg$value <= 0,]$variables %>% unique())
length(neg_var)

mg2 <- mg0[,which(!colnames(mg0) %in% c(neg_var, ident_var))]
mg2[4:123] <- scale(log(mg2[4:123]), center = TRUE, scale = TRUE)
##mg2$index <- rep(c(1,2,3,4), nrow(mg2)/4)

names(mg2)
mg2 <- as.data.frame(mg2 %>%
            group_by(Person,time,Task.Label) %>%
            mutate(index = seq_along(Task.Label))) %>% 
            dplyr::select(-c(age, gender, height, weight, BMI))

# View(mg2[,c("Person","Task.Label","time","index")])
mg_trsscl_l <- melt(mg2, id.vars = c("Person", "time", "Task.Label", "index"), variable.name = "variables")
mg_trsscl_l$variables %>% unique() %>% length()
dat <- list()
for (i in 1:length(task)){
  dat[[i]] <- mg_trsscl_l[which(mg_trsscl_l$Task.Label == task[i]),]
}
```

# NOT RUN --- Variance Component Analysis with scaled values, embedded index, by variable and task

```{r Variance Component Analysis with scaled values, embedded index, by variable and task}

### not run ###

# var <- as.vector(unique(mg$variables))
# task <- sort(as.vector(unique(mg$Task.Label)))
# 
# for(t in 1:16){
# out_mat <- matrix(rep(NA, 6), ncol = 6, nrow = 1)
# for(v in var) {
#   mod <- lmer(value ~ 1 + (1|Person) + (1|time/index), data=dat[[t]][dat[[t]]$variables == v,])
#   re <- as.data.frame(VarCorr(mod))
#   vc_raw <- re$vcov
#   vc_perc <- round(re$vcov / sum(re$vcov)*100,2)
#   ci_mod <- confint(mod)^2
#   ci_l <- (as.data.frame(ci_mod)$`2.5 %`[1:4]) %>% round(2)
#   ci_h <- (as.data.frame(ci_mod)$`97.5 %`[1:4]) %>% round(2)
#   ci <- paste0("(",ci_l, ", ", ci_h,")")
#     
#   vc <- rbind(vc_raw, vc_perc, ci)
#   vc1 <- cbind(vc, matrix(c(rep(v,3), rep(task[t],3)), 3,2))
#   colnames(vc1) <-  c("Person", "Index:Time", "Time", "Unexplained", "Feature", "Task")
#   rownames(vc1) <- c("Variance Component", "% of Total", "Confidence Interval")
#   out_mat <- rbind(out_mat, vc1)
# }
# write.csv(out_mat, paste0(task[t], "_embedded_scledvarcomp.csv"))  
# }
# 
# ##merge 16 individual, by task variance component analysis outputs into one sheet
# Angry <- read.csv("./Embedded/Angry_embedded_scledvarcomp.csv")
# Chewing <- read.csv("./Embedded/Chewing_embedded_scledvarcomp.csv")
# Eye <- read.csv("./Embedded/Eye_embedded_scledvarcomp.csv")
# Eye_Iso <- read.csv("./Embedded/Eye-Iso_embedded_scledvarcomp.csv")
# In_Iso <- read.csv("./Embedded/In-Iso_embedded_scledvarcomp.csv")
# Jaw <- read.csv("./Embedded/Jaw_embedded_scledvarcomp.csv")
# L_Gaze_L <- read.csv("./Embedded/L Gaze-L_embedded_scledvarcomp.csv")
# L_Gaze_R <- read.csv("./Embedded/L Gaze-R_embedded_scledvarcomp.csv")
# Out_Iso <- read.csv("./Embedded/Out-Iso_embedded_scledvarcomp.csv")
# Sad <- read.csv("./Embedded/Sad_embedded_scledvarcomp.csv")
# Smile_Iso <- read.csv("./Embedded/Smile-Iso_embedded_scledvarcomp.csv")
# Surprise <- read.csv("./Embedded/Surprise_embedded_scledvarcomp.csv")
# Swallowing <- read.csv("./Embedded/Swallowing_embedded_scledvarcomp.csv")
# Talk <- read.csv("./Embedded/Talk_embedded_scledvarcomp.csv")
# Up_Gaze <- read.csv("./Embedded/Up Gaze_embedded_scledvarcomp.csv")
# Wrinkle_Iso <- read.csv("./Embedded/Wrinkle-Iso_embedded_scledvarcomp.csv")
# 
# scledtrs_value_varcomp <- rbind(Angry,Chewing,Eye,Eye_Iso,In_Iso,Jaw,L_Gaze_L,L_Gaze_R,Out_Iso,Sad,Smile_Iso,Surprise,Swallowing,Talk,Up_Gaze,Wrinkle_Iso)
# scledtrs_value_varcomp <- scledtrs_value_varcomp[!is.na(scledtrs_value_varcomp$Person),]
# 
# write.csv(scledtrs_value_varcomp,
#           "./Embedded/scledtrs_value_varcomp.csv",
#           row.names = FALSE)
```

# varcomp with scaled embedded by task only

```{r varcomp with scaled embedded by task only}
out_mat <- matrix(rep(NA, 6), ncol = 6, nrow = 1)
for(t in 1:16) {
  mod <- lmer(value ~ 1 +(1|variables) + (1|Person) + (1|time/index), data=dat[[t]])
  re <- as.data.frame(VarCorr(mod))
  vc_raw <- round(re$vcov,2)
  vc_perc <- round(re$vcov / sum(re$vcov)*100,2)
  ci_mod <- confint(mod)^2
  ci_l <- (as.data.frame(ci_mod)$`2.5 %`[1:5]) %>% round(2)
  ci_h <- (as.data.frame(ci_mod)$`97.5 %`[1:5]) %>% round(2)
  ci <- paste0("(",ci_l, ", ", ci_h,")")
    
  vc <- rbind(vc_raw, vc_perc, ci)
  vc1 <- cbind(vc, matrix(rep(task[t],3), 3,1))
  colnames(vc1) <-  c("Variable", "Person", "Index:Time", "Time", "Unexplained", "Task")
  rownames(vc1) <- c("Variance Component", "% of Total", "Confidence Interval")
  out_mat <- rbind(out_mat, vc1)

}
  write.csv(out_mat, "all_embedded_varcomp_scledcov.csv")

```

# Compute ICC and CV by task and variable and save in matrix

```{r Compute ICC and CV by task and variable and save in matrix}
##ICC and CV with Linear Mixed Effect model
task <- sort(as.vector(unique(mg$Task.Label)))
dat <- list()
for (i in 1:length(task)){
  dat[[i]] <- mg[which(mg$Task.Label == task[i]),]
}
var <- as.vector(unique(mg$variables))
task <- sort(as.vector(unique(mg$Task.Label)))

##subjection as random effect

ICClmer_subj <- function(dat) {
  inter <-
    round(summary(lme4::lmer(
      value ~ 1  + age + gender + BMI + time + (1 | Person),
      data = dat
    ))$varcor$Person[1], 4)
  intra <-
    round(summary(lme4::lmer(
      value ~ 1  + age + gender + BMI + time + (1 | Person),
      data = dat
    ))$sigma ^ 2, 4)
  result <- inter / (inter + intra)
  return(result)
}

defaultW <- getOption("warn") 
options(warn = -1) 


#compute CV values by task and by variable
cv.s <- matrix(ncol = 162, nrow = 16, NA)
for (i in 1:16) {
  for (j in 1:162) {
    cv.s[i, j] <-
      EnvStats::cv(dat[[i]][dat[[i]]$variables == var[j], ]$value)
    
  }
}

colnames(cv.s) <- var
rownames(cv.s) <- task
write.csv(cv.s, "cv_bytask.csv", row.names = T)

mg1 <- mg[!mg$variables %in% ident_var,]
var <- as.vector(unique(mg1$variables))
task <- sort(as.vector(unique(mg1$Task.Label)))
dat <- list()
for (i in 1:length(task)){
  dat[[i]] <- mg1[which(mg1$Task.Label == task[i]),]
}

#compute ICC (intr-subject correlation coefficient) values by task and by variable
defaultW <- getOption("warn") 
options(warn = -1) 
resultMat.time <-
  resultMat.subj <-
  resultMat.repeat <- matrix(ncol = 155, nrow = 16, NA)
for (i in 1:16) {
  for (j in 1:155) {
    ##resultMat.time[i,j] <- ICClmer_time(dat[[i]][dat[[i]]$variables == var[j],])
# resultMat.subj[i,j] <- performance::icc(lme4::lmer(
#       value ~ 1  + (1 | Person),
#       data = dat[[i]][dat[[i]]$variables == var[j], ]))$ICC_adjusted
    resultMat.subj[i, j] <- ICClmer_subj(dat[[i]][dat[[i]]$variables == var[j], ])
    ##resultMat.repeat[i,j] <- ICClmer_repeat(dat[[i]][dat[[i]]$variables == var[j],])
  }
}

colnames(resultMat.subj) <- var
rownames(resultMat.subj) <- task
resultMat.subj[is.na(resultMat.subj)] <- 0
ICC.subj <-
  resultMat.subj[, colSums(is.na(resultMat.subj)) < nrow(resultMat.subj)]
write.csv(ICC.subj, "ICC.subj.csv", row.names = TRUE)


# ##time as random effect
# ICClmer_time <- function(dat){
#   inter <- round(summary(lmer(value~ 1  + age + gender + BMI + Person + (1|time),
#                               data=dat))$varcor$time[1],4)
#   intra <- round(summary(lmer(value~ 1  + age + gender + BMI + Person + (1|time),
#                               data=dat))$sigma^2,4)
#   result <- inter / (inter + intra)
#   return(result)
# }
# 
# ##repeat as random effect
# ICClmer_repeat <- function(dat){
#   inter <- round(summary(lmer(value~ 1  + age + gender + BMI + Person + (1|index),
#                               data=dat))$varcor$index[1],4)
#   intra <- round(summary(lmer(value~ 1  + age + gender + BMI + Person + (1|index),
#                               data=dat))$sigma^2,4)
#   result <- inter / (inter + intra)
#   return(result)
# }


# resultMat.time[is.na(resultMat.time)] <- 0
# resultMat.repeat[is.na(resultMat.repeat)] <- 0

# ICC.time <- resultMat.time[,colSums(is.na(resultMat.time))<nrow(resultMat.time)]
# ICC.rep <- resultMat.repeat[,colSums(is.na(resultMat.repeat))<nrow(resultMat.repeat)]
# write.csv(ICC.time,"ICC.time.csv",row.names = TRUE)
# write.csv(ICC.rep,"ICC.rep.csv",row.names = TRUE)

```

# Draw ICC and CV Heatmap

```{r Draw ICC and CV Heatmap}
rm <- setdiff(var, colnames(ICC.subj))

##Preparte ICC heatmap
impute.mean <-
  function(x)
    replace(x, is.na(x) |
              is.nan(x) |
              is.infinite(x), mean(x[!is.na(x) & !is.nan(x) & !is.infinite(x)]))
impute.na <-
  function(x)
    replace(x, is.na(x) | is.nan(x) | is.infinite(x), NA)
ICC.subj <- sapply(data.frame(ICC.subj), as.numeric)
resultMat.subj[is.infinite(resultMat.subj)] <- 1
resultMat.subj[is.na(resultMat.subj)] <- 0
# ICC.subj <- apply(resultMat.subj, 1, impute.mean)
# ICC.subj.abs <- abs(resultMat.subj)
ICC.subj.abs <- abs(ICC.subj)
# ICC.subj.abs[ICC.subj.abs >=1] <- 1
sum(apply(ICC.subj, 2, function(.) sum(is.infinite(.))))

resultMat.subj <- resultMat.subj[,!colnames(resultMat.subj) %in% c("Event.Duration..s.","Perceptible.Onset.Time..s.")]
split_rows <-  c(rep("EMG", 56), rep("EEG", 48), rep("EOG", 50))
pdf("Supplementary Figure 2_ICC.pdf",
    height = 10,
    width = 15)
ComplexHeatmap::Heatmap(
  t(resultMat.subj),
  row_split = split_rows,
  row_title = c("EMG", "EEG", "EOG"),
  row_names_gp = gpar(fontsize = 0),
  name = "ICC between Subjects",
  col = c("white", "red")
)
dev.off()

# pdf("ICC_time.pdf", height = 10, width = 15)
# Heatmap(t(resultMat.time), row_split = split_rows, row_title = c("EMG", "EEG", "EOG"), row_names_gp = gpar(fontsize = 0), name = "ICC between Measured Times", col = c("white", "red"))
# dev.off()
# 
# pdf("ICC_repeat.pdf", height = 10, width = 15)
# Heatmap(t(resultMat.repeat), row_split = split_rows, row_title = c("EMG", "EEG", "EOG"), row_names_gp = gpar(fontsize = 0), name = "ICC between Repeats", col = c("white", "red"))
# dev.off()


##Prepare CV heatmap
cv.all <- cv.s * 100
cv.all <- abs(cv.all)
cv.all <- cv.all[,!colnames(cv.all) %in% c("Event.Duration..s.","Perceptible.Onset.Time..s.")]

##cv.all <- apply(cv.all, 2, impute.mean)
sum(apply(cv.all, 2, function(.)
  sum(is.infinite(.))))
mycols <- circlize::colorRamp2(breaks = c(0, 40, 100),
                               colors = c("blue", "white", "red"))


split_rows <-  c(rep("EMG", 56), rep("EEG", 52), rep("EOG", 52))
pdf("Supplementary Figure 3_CV.pdf",
    height = 10,
    width = 15)
ComplexHeatmap::Heatmap(
  t(cv.all),
  row_split = split_rows,
  row_title = c("EEG", "EMG","EOG"),
  row_names_gp = grid::gpar(fontsize = 0),
  name = "Coefficient of Variation (%)",
  col = mycols
)
dev.off()

# abs_cv <- abs(cv.s)
# mycols <- colorRamp2(breaks = c(0, 8, 10),
#                      colors = c("blue", "white", "red"))
# pdf("cv2.pdf", height = 10, width = 15)
# Heatmap(
#   t(abs_cv),
#   row_split = split_rows,
#   row_title = c("EMG", "EEG", "EOG"),
#   row_names_gp = gpar(fontsize = 0),
#   name = "Coefficient of Variation",
#   col = mycols
# )
# dev.off()
```

# Summary Stats for each Variable

```{r Summary Stats for each Variable}
summary_mg_variables <- summary(mg0[,-c(1,2,3)])
summ_sd <- sapply(mg0[,-c(1,2,3)], sd, na.rm=TRUE) %>% as.vector
summ_sd <- round(summ_sd, 2) 
summ_sd <- paste0("SD: ", summ_sd) %>% t()

write.csv(summary_mg_variables, "variable_summary.csv", row.names = F)
write.csv(summ_sd, "variable_sd.csv", row.names = F)

```

